### 2015-06-09 text/ms.Rmd
Add to methods and results

\begin{equation}
\hat{B}_{t+1} = B_t + r B_t \left(1 - B_t / B_0 \right) - C_t,
\end{equation}

@@

@@

$$
\hat{\theta} = 
\mathrm{argmin}_\theta \left( L(b \, | \, \hat{b}_{\mathrm{ensemble}}) \right)
$$
$$
\hat{b}_\mathrm{ensemble} = 
f \left( \hat{b}_\mathrm{CMSY}, \hat{b}_\mathrm{COM-SIR}, 
\hat{b}_\mathrm{SSCOM}, \hat{b}_\mathrm{mPRM}, 
S(0.2), S(0.5), | \, \theta \right)
$$

\noindent where $L$ is a generalized loss function, $f$ is some generalized
regression function, $\hat{b}_\mathrm{CMSY}$ is the prediction from the CMSY
model etc., $b$ is the true value the model is fitted to, $S(n)$ represents the
spectral density at frequency $n$ of the scaled catch series, and $\theta$ is
the set of parameters for the regression function. For all ensemble models of
mean \bbmsy\\, which is bounded at zero, we fit the models in log space and
exponentiated the predictions to derive a median estimate of \bbmsy\\. For the
estimates of \bbmsy\\ slope we fit ensemble models on the natural untransformed
scale.

We calculated the average ensemble models as the geometric mean of the
individual model median \bbmsy\\ estimates and the mean of the individual model
\bbmsy\\ slopes. We fit the linear model ensemble with second-order
interactions.

We fit two machine learning ensemble models based on regression trees.
Regression trees sequentially determine what value of a predictor best splits
the response data into two 'branches' based on a specified loss function. In
random forests, a series of regression trees are built on a random subset of
the data and random subset of the covariates of the model (REF). In generalized
boosted models (GBMs), each subsequent model is fit to the residuals from the
previous model; data points that are fit poorly in a given model are given more
weight in the next model [@elith2008]. Random forests and GBMs can provide
strong predictive performance and fit highly non-linear relationships (REFs).
We fit random forest models with the **randomForest** package [@liaw2002] for
\textsf{R} with the default argument values. We fit boosted regression tree
models with the **GBM** package [@ridgeway2015] for \textsf{R}. Based on
cross-validation with the **caret** package (Supporting Materials, Fig. SX), we
fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate
(shrinkage parameter) of $0.01$, and all other arguments at their default
values.

@@

Individual model and ensemble model scatterplots:
Fig. \ref{fig:hexagon}

Accuracy, rank correlation, and bias:
Fig. \ref{fig:performance}

>>>>

$$\hat{B}_{t+1} = B_t + r B_t \left(1 - B_t / B_0 \right) - C_t,$$

@@

<!--TODO: build in fig:didactic -->

@@

$$
\hat{\theta} = 
\mathrm{argmin}_\theta \left( L(b \, | \, \hat{b}_{\mathrm{ensemble}}) \right)
$$
$$
\hat{b}_\mathrm{ensemble} = 
f \left( \hat{b}_\mathrm{CMSY}, \, \hat{b}_\mathrm{COM-SIR}, \,
\hat{b}_\mathrm{SSCOM}, \, \hat{b}_\mathrm{mPRM}, \,
S(0.2), \, S(0.5), \, | \, \theta \right)
$$

\noindent where $L$ is a generalized loss function, $f$ is some generalized
regression function, $\hat{b}_\mathrm{CMSY}$ is the prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $b$ is the true value the model is
fitted to, $S(n)$ represents the spectral density at frequency $n$ of the
scaled catch series, and $\theta$ is the set of parameters for the regression
function. For all ensemble models of mean \bbmsy\\, which is bounded at zero,
we fit the models in log space and exponentiated the predictions to derive a
median estimate of \bbmsy\\. For the estimates of \bbmsy\\ slope we fit
ensemble models on the natural untransformed scale.

We calculated the average ensemble models as the geometric mean of the
individual model median \bbmsy\\ estimates and the mean of the individual model
\bbmsy\\ slopes. We fit the linear model ensemble with second-order
interactions. We fit two machine learning ensemble models based on regression
trees. Regression trees sequentially determine what value of a predictor best
splits the response data into two 'branches' based on a specified loss
function. In random forests, a series of regression trees are built on a random
subset of the data and random subset of the covariates of the model (REF). In
generalized boosted models (GBMs), each subsequent model is fit to the
residuals from the previous model; data points that are fit poorly in a given
model are given more weight in the next model [@elith2008]. Random forests and
GBMs can provide strong predictive performance and fit highly non-linear
relationships (REFs). We fit random forest models with the **randomForest**
package [@liaw2002] for \textsf{R} with the default argument values. We fit
boosted regression tree models with the **GBM** package [@ridgeway2015] for
\textsf{R}. Based on cross-validation with the **caret** package (Supporting
Materials, Fig. SX), we fit GBMs with 2000 trees, an interaction depth of $6$,
a learning rate (shrinkage parameter) of $0.01$, and all other arguments at
their default values.

@@

* Individual model and ensemble model scatterplots:
Fig. \ref{fig:hexagon}

* Accuracy, rank correlation, and bias:
Fig. \ref{fig:performance}

* Regression coefficients from linear model ensemble:
Fig. \ref{fig:lm-coefs}

* Partial dependence plots of GBMs:
Fig. \ref{fig:partial-sim}

* Partial residuals version of GBMs:
Fig. \ref{fig:partial-residuals-sim-gbm}

* 2-dimension partial dependence plots:
Fig. \ref{fig:partial-2d-sim}

* ROC curves from simulation ensembles:
Fig. \ref{fig:roc-sim}

* Scatterplots of RAM fits:
Fig. \ref{fig:hexagon-ram}

* Scatterplots of basic ensembles without covariates:
Fig. \ref{fig:hexagon-sim-basic}

* Scatterplots estimating slope:
Fig. \ref{fig:scatter-sim-slope}

* Accuracy, rank correlation, and bias of slope:
Fig. \ref{fig:performance-sim-slope}
